6CCS3PRJ \\\vspace{0.5cm} A Pragmatic Infrastructure Modelling and Verification Framework

### 2014-04-14 paper.tex
More on dynamic infra

\pagebreak
\subsection{Hosts}
Hosts are a simple structure, they are conceptually just an instance of the management agent running on a physical or virtual server. When the management software is installed, the user can specify an environment, e.g.\ development, staging or production. Hosts are added and removed based upon the `setup' and `remove' functions of the management agent.

\begin{listing}[h]
\begin{minted}[fontfamily=fi4]{json}
  {
    "hostname": "db-1.local",
    "ip": "192.168.1.100",
    "environment": "development",
    "service_id": 3,
    "status": "ok"
  }
\end{minted}
\end{listing}

>>>>

\pagebreak
\subsection{Hosts}
Hosts are a simple structure, they are conceptually just an instance of the management agent running on a physical or virtual server. When the management software is installed, the user can specify an environment, e.g.\ development, staging or production. Hosts are initially registered via the `setup' command of the management agent, and are associated/dissociated with services when the `start' and `stop' monitoring commands are used, specifying a particular service specification. Hosts are considered transient, they are instances of an application running at a particular time. This is particularly true of more dynamic infrastructure such as auto-scaling groups.

\begin{listing}[h]
\begin{minted}[fontfamily=fi4]{json}
  {
    "hostname": "db-1.local",
    "ip": "192.168.1.100",
    "environment": "development",
    "service": "example-service",
    "status": "ok"
  }
\end{minted}
\end{listing}
